A formalization of semi-simplicial and semi-cubical sets

### 2023-01-06 paper/paper.tex
paper: minor polish

\title{A formalization of semi-simplicial and semi-cubical sets}
\author{
  \textcolor{gray80}{Hugo Herbelin} \\
  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
  \and
  \textcolor{gray80}{Ramkumar Ramachandra} \\
  \itshape \textcolor{gray80}{Université Paris-Cité, Inria, CNRS, IRIF, Paris}
}
\date{}

@@

\section{Overture}
In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type. Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of (Kreisel) realizability~\cite{bernardy12,moulin16}. It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.

@@

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.3\linewidth}|p{.3\linewidth}|p{.3\linewidth}}
    \toprule
            & Set theory  & Type theory \\
    \graymidrule
    Fibered & \cite{cchm} &             \\
    \graymidrule
    Indexed &             & Our work    \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

\title{A formalization of semi-simplicial and semi-cubical sets}
\author{
  \textcolor{gray80}{Hugo Herbelin} \\
  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
  \and
  \textcolor{gray80}{Ramkumar Ramachandra} \\
  \itshape \textcolor{gray80}{Université Paris Cité, Inria, CNRS, IRIF, Paris}
}
\date{}

@@

\section{Overture}
In the context of typed functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational equality of programs of this type. Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity has a cubical flavor~\cite{johann17,altenkirch15,moulin16}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates instead of relations, in which case we obtain a form of realizability~\cite{bernardy12,moulin16}. It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Observation from Hugo Moeneclaey}.

@@
